---
title: "Data Visualisation Final Project"

output:
  flexdashboard::flex_dashboard:
    # storyboard: true
    orientation: columns
    vertical_layout: fill
    
    theme:
      version: 4
      bootswatch: bootstrap
---


```{r}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = FALSE
)
```



```{r figure details}

title.size <- 16
subtitle.size <- 12
axis.title.size <- 10
axis.text.size <- 8


```


```{r setup}
library(flexdashboard)
```

```{r libraries, echo=FALSE}
library(bslib)
library(skimr)
library(vroom)
library(tidyverse)
library(dplyr)
library(ggthemes)
library(gghighlight)
library(plotly)
library(patchwork)
library(countrycode)
library(jpeg)
library(png)
library(grid)


```

```{r echo=FALSE}

astronauts <- vroom('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-14/astronauts.csv')

launches <- vroom("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/launches.csv")

agencies <- vroom("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/agencies.csv")

mission_success <- vroom(here::here("data","Space_Corrected.csv"))
```


```{r echo=FALSE, include=FALSE}
mission_success <- select(mission_success, -c(1,2))

mission_success <- mission_success %>% 
  janitor::clean_names() %>% 
  mutate(datum = as.Date(mission_success$Datum, format = "%a %b %d, %Y"))


launches <-  launches %>% 
  left_join(mission_success, by = c("launch_date" = "datum"))
```

```{r, echo=FALSE, include=FALSE}
country_names <- c(US = "United States",
                'F'  = "France",
                BR = "Brazil",
                CN = "China",
                I = "italy",      
                'I-ESA' = "European Space Agency",
                RU  = "Russia",
                IR = "Iran",
                IL = "Isreal",
                J = "Japan",
                IN = "India",
                KR = "North Korea",
                KP = "South Korea",
                SU = "Soviet Union",
                UK = "United Kingdom",
                CYM = "Cayman Islands",
                'I-ELDO' = "European Launcher Development Organisation")  


country_colors <- c(US = "blue",
                    'F'  = "skyblue",
                    BR = "limegreen",
                    CN = "red3",
                    I = "lightgreen",      
                    'I-ESA' = "plum1",
                    RU  = "tomato",
                    IR = "lightgoldenrod",
                    IL = "tan2",
                    J = "mistyrose",
                    IN = "",
                    KR = "North Korea",
                    KP = "South Korea",
                    SU = "Soviet Union",
                    UK = "United Kingdom",
                    CYM = "Cayman Islands",
                    'I-ELDO' = "European Launcher Development Organisation")



launches <- launches %>% 
  mutate(country_name = country_names[state_code])

launches <- launches %>% 
  mutate(agency = case_when(is.na(agency) ~ state_code,
                            TRUE ~ agency))

```
# Introduction

## Column 1 

### Introduction


<center>
<font size="+6">
<br>
<br>
<br>
<br>
<br>
**To infinity and Beyond** - Stories from Space and about Astronauts
<br>
<br>
</font>
</center>

<center>
<font size="+2">
*Authors: * *Kazmer Nagy-Betegh, Nisa Ozer, Lauren Wade, Chandrima Tolia, Nereid Kwok, Thomas Giannetti*
</font>
</center>



# Countries Launching Rockets

## Column 1

Let us look at the number of launches by Country. You can see a seperation between the US and Soviet Union, launching significantly more during the cold war. These two countries kickstarted space exploration during the sixties so let us look at that weird and exciting time.

### Launches by Countries


```{r space_race1, fig.height= 5, fig.width= 11, fig.align='center'}

launches %>% 
  filter(country_name == "NA")

space_race <- launches %>% 
  # filter(state_code %in% c("US", "SU", "RU")) %>% 
  group_by(launch_year, country_name) %>% 
  summarise(state_code, country_name, num_launches = n()) %>% 
  ungroup()
  


launchs_per_year_US_SU <- space_race %>% 
  filter(state_code %in% c("US", "SU", "RU")) %>% 
  ggplot( aes(x = launch_year,
              y = num_launches))+
  geom_point(aes(color = country_name))+
  geom_line(aes(color = country_name))+
  gghighlight(state_code %in% c("US","SU","RU"))+
  theme_minimal()+
  labs(title = "United States and Soviet Union (Russia) Space Race",
       x = "",
       y = "launches/year")
  # scale_color_manual(values = country_colors)



launchs_per_year_non_us_su <- space_race %>% 
  ggplot(aes(x = launch_year,
              y = num_launches))+
  geom_point(aes(color = country_name))+
  geom_line(aes(color = country_name))+
  gghighlight(!state_code %in% c("US","SU","RU"))+
  theme_minimal()+
  labs(title = "Countries joining Space Exploration",
       x = "",
       y = "launches/year")
  # scale_color_manual(values = country_colors)

launchs_per_year_US_SU  | launchs_per_year_non_us_su

```


# Space Race Dates

## Column 1

### Space race dates marked {data-height=300}

```{r space_race, fig.width=16}

img <- readJPEG(here::here("data/milky.jpg"))

g <- rasterGrob(img, interpolate=TRUE)

space_race_dates <- space_race %>% 
  filter(state_code %in% c("US", "SU", "RU")) %>% 
  ggplot( aes(x = launch_year,
              y = num_launches))+
  geom_point(aes(color = country_name))+
  geom_line(aes(color = country_name))+
  gghighlight(state_code %in% c("US","SU","RU"))+
  theme_minimal()+
  labs(title = "1957 - 1969 Space Race",
       x = "",
       y = "launches/year")+
  annotate("rect", xmin = 1957, xmax = 1969, ymin = 0, ymax = 110,
           alpha = 0.3, fill = "skyblue")+
  theme(plot.title = element_text(size = title.size*7/3),
        axis.title = element_text(size = axis.title.size),
        axis.text = element_text(size = axis.text.size))


space_race_dates
```

### Space Race Key Dates {data-height=700}

```{r fig.width=12}

space_race_mission_success_values <- launches %>% 
  group_by(launch_year, country_name, category) %>% 
  summarise(n_missions = n()) %>% 
  mutate(mission_ssuccess_rate = round(n_missions/sum(n_missions)*100,2)) %>% 
  ungroup() %>% 
  filter(category == "O") %>% 
  select(-n_missions, -category)

launches <- launches %>% 
  left_join(space_race_mission_success_values, by = c("country_name" = "country_name","launch_year" = "launch_year"))

img <- readJPEG(here::here("data/laika.jpg"))

g <- rasterGrob(img, interpolate=TRUE)


img <- readJPEG(here::here("data/alex.jpg"))

g2 <- rasterGrob(img, interpolate=TRUE)

img <- readJPEG(here::here("data/moon.jpg"))

g3 <- rasterGrob(img, interpolate=TRUE)

launches %>% 
  filter(state_code %in% c("US", "SU", "RU")) %>% 
  filter(launch_year < 1970) %>% 
  group_by(launch_year, country_name) %>% 
  summarise(mission_ssuccess_rate, launch_year, country_name, num_launches = n()) %>% 
  ggplot( aes(x = launch_year,
              y = num_launches,
              label = mission_ssuccess_rate))+
  
  annotate("rect", xmin = 1957, xmax = 1969, ymin = 0, ymax = 180,
           alpha = 0.3, fill = "skyblue")+
  
  annotation_custom(g, xmin=1955, xmax=1959, ymin=57, ymax=80)+
  annotate("segment", x = 1957, y = 0, xend = 1957, yend = 50 ,color = "tomato")+
  annotate("text", x = 1957, y = 55, label = "Laika in Space",color = "tomato")+
  
  annotate("segment", x = 1961, y = 0, xend = 1961, yend = 70 , color = "tomato")+
  annotate("text", x = 1961, y = 75, label = "Yuri Gagarin in Space", color = "tomato")+
  
  annotate("segment", x = 1963, y = 0, xend = 1963, yend = 90 , color = "tomato")+
  annotate("text", x = 1963, y = 95, label = "Valentina Tereshkova first woman in Space", color = "tomato")+
  
  annotation_custom(g2, xmin=1964, xmax=1966, ymin=108, ymax=128)+
  annotate("segment", x = 1965, y = 0, xend = 1965, yend = 100 , color = "tomato")+
  annotate("text", x = 1965, y = 105, label = " Alexei Leonov leaves spacecrafts and has first spacewalk", color = "tomato")+
  
  annotate("segment", x = 1967, y = 0, xend = 1967, yend = 110 , color = "black")+
  annotate("text", x = 1967, y = 115, label = "Deadliest Year for both Sides", color = "black")+
  
  annotate("segment", x = 1968, y = 0, xend = 1968, yend = 130 , color = "blue")+
  annotate("text", x = 1968, y = 132, label = "Apollo 8 first human crewed spacecraft to reach the moon, orbit, and return to earth", color = "blue", hjust = .8)+
  
  annotation_custom(g3, xmin=1968, xmax=1969, ymin=142 ,ymax=172)+
  annotate("segment", x = 1969, y = 0, xend = 1969, yend = 135 , color = "blue")+
  annotate("text", x = 1969, y = 140, label = "First men to walk on the moon - American victory", color = "blue", hjust = 1)+
  
  geom_point(aes(color = country_name))+
  geom_line(aes(color = country_name))+
  geom_text(aes(x = launch_year,
              y = num_launches,
              label = paste0(mission_ssuccess_rate,"%")),
            vjust = -1)+
  theme_minimal()+
  labs(title = "1957 - 1969 Space Race",
       subtitle = "Percentages indicate the success rate of launches in each year",
       x = "",
       y = "launches/year",
       color = "")+
  xlim(1955,1972)+
  ylim(0,180)+
  scale_x_continuous(breaks = scales::pretty_breaks(12))+
  theme(plot.title = element_text(size = title.size),
        axis.title = element_text(size = axis.title.size),
        axis.text = element_text(size = axis.text.size))
  

```



# Slide 3

```{r}


space_race_mission_success <- launches %>% 
  filter(state_code %in% c("US", "SU", "RU")) %>%
  filter(launch_year < 1970) %>% 
  group_by(launch_year, country_name, category) %>% 
  summarise(n_missions = n()) %>% 
  mutate(prc_missions = round(n_missions/sum(n_missions)*100,2)) %>% 
  ggplot(aes(x = country_name,
              y = n_missions))+
  geom_col(aes(fill = category))+
  geom_text(aes(x = country_name,
                y = n_missions,
                label = paste0(prc_missions,"%"),
                group = category),
            position=position_stack(vjust=0.5))+
  theme_minimal()+
  labs(title = "1957 - 1969 Space Race success Rate",
       x = "",
       y = "launches/year",
       fill = "")+
  facet_grid(~launch_year)+
  scale_fill_manual(label = c("Failed Mission", "Succesful Mission"),
                    values = c("tomato","springgreen4"))+
  theme(axis.text.x = element_text(angle= 45, ))

space_race_mission_success
```

# Slide 4

```{r}
age <- astronauts %>% 
  mutate(age_at_mission = year_of_mission - year_of_birth) %>% 
  select(age_at_mission, year_of_mission, year_of_birth, name) %>%
  mutate(decade = case_when((year_of_mission >= 1960 & year_of_mission < 1970) ~ "1960s",
                            (year_of_mission >= 1970 & year_of_mission < 1980) ~ "1970s",
                            (year_of_mission >= 1980 & year_of_mission < 1990) ~ "1980s",
                            (year_of_mission >= 1990 & year_of_mission < 2000) ~ "1990s",
                            (year_of_mission >= 2000 & year_of_mission < 2010) ~ "2000s",
                            (year_of_mission >= 2010 & year_of_mission < 2020) ~ "2010s"))

age_first <- age %>% 
  group_by(name) %>% 
  summarise(age_at_mission = min(age_at_mission), decade)

#age at their first mission, when they become astronauts
age_first_plot <- age_first %>% 
  ggplot(aes( x = age_at_mission, fill=decade )) +
  geom_histogram()+
  labs(title = "Astronauts Have Started Their Career Later Overtime",
       subtitle = "Age taken for each astronaut at the time of their first mission",
       x="Age at Mission",
       y="Number of Austronauts") +
  facet_wrap(~decade)+
  theme_minimal()


#general age distribution in the industry
age_plot <- age %>% 
  ggplot(aes( x = age_at_mission, fill=decade )) +
  geom_histogram() +
  labs(title = "Astronauts Have Gotten Older Overtime",
       subtitle = "Age taken for each astronaut at time of every mission",
        x="Age at Mission",
       y="Number of Austronauts") +
  theme_minimal() +
  facet_wrap(~decade)
 
age_first_plot / age_plot
```

# Slide 5

```{r }

gender_count <- astronauts %>% 
    group_by(sex, year_of_mission) %>% 
    count(year_of_mission)

female_male <- gender_count %>% 
  ggplot(aes(x = year_of_mission, y = n, fill = sex)) +
  geom_col() +
  labs(title = "Women Start Going to Space in the 80s",
       subtitle = "Data taken for each austronaut at time of every mission",
       x="Year of Mission",
       y="Number of Austronauts")+
  theme_minimal()

female_male_annotated <- female_male + 
  annotate("text", x = 1965, y = 25, label = "Valentina Tereshkova", size = 3) + 
  annotate("segment", x = 1965, xend = 1963, y = 23,  yend = 6, colour = "black", size = 0.5 , arrow = arrow() )

female_male_annotated + scale_x_continuous(breaks=seq(1960,2020,5)) + 
  geom_text(aes(label = n), vjust = -0.2, size =4)
    
```

# Slide 5



# Slide

```{r space walk record holders, fig.align='center', fig.height= 5, fig.width= 11, echo=FALSE}

astronauts %>% 
  group_by(name) %>% 
  distinct(nationality, total_eva_hrs) %>% 
  ungroup() %>% 
  slice_max(order_by = total_eva_hrs, n=15, with_ties = TRUE) %>% 
  ggplot()+
  geom_col(aes(x = total_eva_hrs,
             y = reorder(name,total_eva_hrs),
             fill = nationality))+
  geom_text(aes(x = total_eva_hrs,
             y = reorder(name,total_eva_hrs),
             label = total_eva_hrs),
            hjust = 2)+
  theme_minimal()+
  labs(title = "Most Hours Spent Space Walking",
       y = "",
       x = "hours")
  
  



```

# Slide

US Launches

1966: Peaked state launches 1986: Challenger Explosion 1989: Private commercial Launches starts 2012: Barely any state launches

```{r }
 launches %>% 
  filter(state_code == "US") %>% 
  mutate(agency_type = ifelse(as.character(agency_type) == "startup", "private", as.character(agency_type))) %>%  # combine startup and private
  group_by(launch_year,agency_type,category) %>% 
  count() %>% 
  unite('type_category',agency_type:category,remove=FALSE) %>% 
  mutate(type_category = case_when(type_category=="state_F" ~ "State - Failure",
                                   type_category=="state_O" ~ "State - Success",
                                   type_category=="private_F" ~ "Private - Failure",
                                   type_category=="private_O" ~ "Private - Success")) %>% 
  ggplot(aes(x=launch_year,y=n,fill = type_category))+
  geom_col(width = 0.8)+
  geom_segment(aes(x = 1966, y = 85, xend = 1966, yend = 78),color = "royalblue",
                  arrow = arrow(length = unit(0.15, "cm")))+
  geom_segment(aes(x = 1986, y = 40, xend = 1986, yend = 15),color = "indianred",
                  arrow = arrow(length = unit(0.15, "cm")))+
  geom_segment(aes(x = 1989, y = 60, xend = 1989, yend = 20),color = "grey40",
                  arrow = arrow(length = unit(0.15, "cm")))+
  geom_segment(aes(x = 2012, y = 42, xend = 2012, yend = 20),color = "royalblue",
                  arrow = arrow(length = unit(0.15, "cm")))+
  annotate("text", x=1966, y=88, label= "1966: Highest State Launches",size=3.5, color="royalblue3") +
  annotate("text", x=1986, y=48, label= "1986:\n Challenger \n Explosion",size=3.5, color="indianred3") +
  annotate("text", x=1989, y=63, label= "1989: Private Launches Begins",size=3.5, color="grey30") +
  annotate("text", x=2012, y=45, label= "2012: State Launches Faded",size=3.5, color="royalblue3") +
  annotate("text", x=1959, y=69, label= "High failure rates \n in early years",size=3.5,color="lightblue4") +
  labs(title = "US State Launches Falls while Private Launches Rises",
       subtitle = "US State and Private Launches by Success",
       x="Year",
       y="Launches",
       fill="Agency Success")+
  theme_minimal()+
  scale_fill_manual("Agency Success", 
                    values = c("State - Failure" = "lightblue", 
                               "State - Success" = "dodgerblue",
                               "Private - Failure" = "grey", 
                               "Private - Success" = "black"))+
  theme(legend.title = element_text( size=8), legend.text=element_text(size=8), legend.background = element_rect(color = NA))

```

General: High spending/budget during Space Race. Drastic decrease of spending/budget once space is over. US-USSR Space Race: Budget higher than actual spending (underbudget), NASA is too ambitious 2012 paused launches: Budget are increasing, ...

# Slide

```{r}
# Import and clean Nasa Spending Data
nasa_spending <- vroom(here::here("data","nasa_budget.csv"))
nasa_spending <- nasa_spending %>% 
  select(1:6) %>%  # select non empty rows
  janitor::clean_names() %>% 
  mutate(request = as.numeric(request),
         actual = as.numeric(actual))

# Graph of NASA actual vs budget spending
nasa_spending %>% 
  ggplot(aes(x=fiscal_year))+
  geom_line(data=subset(nasa_spending, fiscal_year>=2021),aes(y=request),linetype=2,color="royalblue",size=1) +
  geom_line(data=subset(nasa_spending, fiscal_year<=2021),aes(y=request),linetype=1,color="orchid") +
  geom_line(aes(y=actual),size=1,color="royalblue")+
  geom_vline(xintercept = 2012,color="grey50",linetype="dashed")+
  geom_vline(xintercept = 1959,color="grey50",linetype="dashed")+
  geom_vline(xintercept = 1975,color="grey50",linetype="dashed")+
  geom_ribbon(aes(ymin=request, ymax=pmax(actual,request)),fill="red", alpha = 0.3) +
  geom_ribbon(aes(ymin=pmin(actual,request), ymax=request), fill="turquoise4", alpha = 0.3)+
  annotate("rect", xmin = 1959, xmax = 1975, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.1) +
  annotate("rect", xmin = 2021, xmax = 2026, ymin = -Inf, ymax = Inf, fill = "wheat", alpha = 0.3)+
  annotate("text", x=2023.6, y=3550, label= "Forecasted \n Budget",size=3.1, color="royalblue3") +
  annotate("text", x=2012.1, y=500, label= " NASA paused \n self-launching \n missions from 2012",size=3.1, color="grey20",hjust = 0) +
  annotate("text", x=1967, y=300, label= "US-USSR Space Race",size=3.5, color="grey20") +
  labs(title = "NASA Budget vs Actual Spending",
       subtitle = "NASA Spending Compared to Budget (Inflation Adjusted)",
       x="Year",
       y="USD (Million)")+
  theme_minimal()

```

state and private launches success/failure rate (spaceX) NASA fails, budget cut, blow stuff up cheaper
